---
title: "2nd Year Workshop"
subtitle: "Tips for generating research ideas"
author: Ian McCarthy, Emory University
date: Economics PhD Professionalism Workshop #"`r format(Sys.time(), '%d %B %Y')`"
header-includes: 
  - \usepackage{graphicx}
  - \usepackage{amsmath}
  - \usepackage{includepdf}  
output:
#  html_document: default (toggle on for "simplified" view)
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom.css] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: ["macros.js","https://platform.twitter.com/widgets.js"]
---
class: inverse, center, middle
name: ideas

# Where to get ideas?

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>


<!-- Adjust some CSS code for font size, maintain R code font size -->
<style type="text/css">
.remark-slide-content {
    font-size: 30px;
    padding: 1em 2em 1em 2em;    
}
.remark-code, .remark-inline-code { 
    font-size: 20px;
}
</style>


<!-- Set R options for how code chunks are displayed and load packages -->
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
options(dplyr.summarise.inform = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center",  
  fig.height=3, #fig.width=6,
  # out.width="748px", #out.length="520.75px",
  dpi=300, #fig.path='Figs/',
  cache=T#, echo=F, warning=F, message=F
  )

knitr::opts_hooks$set(fig.callout = function(options) {
  if(options$fig.callout) {
    options$echo = FALSE
  }
  options
})

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, xaringanExtra, webshot)
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble(rgb(0.9, 0.5, 0.5))
```

---
# Where to get ideas?

1. Read non-academic policy papers/briefs
    - Commonwealth Fund
    - Petersen-KFF
    - Health Affairs or NEJM Opinion Pieces
    - Newspapers


---
count: false

# Where to get ideas?

2. Academic papers and survey articles
    - Read the abstract and skim the rest
    - JEP and JEL are good for survey articles
    - Get TOC notifications from relevant journals
    - NBER working papers


---
count: false

# Where to get ideas?

3. Seminars
    - Attend and read papers in advance
    - Meet with speakers and ask questions



---
count: false

# Where to get ideas?

4. Faculty
    - Be engaged in classes...think about potential research ideas
    - Schedule meetings and come with some questions



---
count: false

# Where to get ideas?

5. Peers
    - Ask questions and throw out some ideas
    - Learn from each other




---
class: inverse, center, middle
name: ideas2

# What to do with your ideas

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>


---
# What to do with ideas?

1. Keep track of them!
