---
title: "2nd Year Workshop"
subtitle: "From idea to project"
author: Ian McCarthy, Emory University
date: Economics PhD Professionalism Workshop #"`r format(Sys.time(), '%d %B %Y')`"
header-includes: 
  - \usepackage{graphicx}
  - \usepackage{amsmath}
  - \usepackage{includepdf}  
output:
#  html_document: default (toggle on for "simplified" view)
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom.css] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: ["macros.js"]
---
class: inverse, center, middle
name: project

# From idea to "proposal"

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>


<!-- Adjust some CSS code for font size, maintain R code font size -->
<style type="text/css">
.remark-slide-content {
    font-size: 30px;
    padding: 1em 2em 1em 2em;    
}
.remark-code, .remark-inline-code { 
    font-size: 20px;
}
</style>


<!-- Set R options for how code chunks are displayed and load packages -->
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
options(dplyr.summarise.inform = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center",  
  fig.height=3, #fig.width=6,
  # out.width="748px", #out.length="520.75px",
  dpi=300, #fig.path='Figs/',
  cache=T#, echo=F, warning=F, message=F
  )

knitr::opts_hooks$set(fig.callout = function(options) {
  if(options$fig.callout) {
    options$echo = FALSE
  }
  options
})

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, xaringanExtra, webshot)
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble(rgb(0.9, 0.5, 0.5))
```

---
# Key steps

1. What is the research *question*?
2. What is the hook?
3. What is your economic model or framework?
4. What is your data and identification strategy?

---
# 1. The question

From Jesse Shapiro's [Four Steps to an Applied Micro Paper](https://scholar.harvard.edu/files/shapiro/files/foursteps.pdf):

- The question has an answer
- The answer is not obvious
- The answer is actionable/relevant



---
# 2. The hook

Why is your question important and relevant? This should be aimed at a general audience, not someone specific to your field and perhaps not even to an economist.


---
# 3. The model


- Question should be specific enough so that you are able to write down a model, an equation, or a series of equations that would facilitate answering this question
- **Not** simply a mathematical representation of your research question...it should help inform the empirical methods and variation you will be using


---
# 4. Data and identification strategy

- What data do you plan to use?
- Where is the variation in the data that will identify the effect of interest? How does such variation lend a credible identification strategy?
- How does your data and identification address your original question?
- Need to know that the data exists and how to access it (within a reasonable time period/cost)


---
# Repeat

- Repeat this process a handful of times
- Discuss the ideas with classmates and faculty
- Identify your best proposals and move to the next stage

---
class: inverse, center, middle
name: plan

# From proposal to plan

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>

---
# The research plan

- Plan consists of the proposal plus...
- The "value-added"

---
# The value-added

- What do we know in the literature about this problem? 
- What are the relevant papers when it comes to the topic, methods, and data? 
- How exactly do you contribute to the literature, above and beyond what was already done? 

--

Doing the same thing for a different population or using different methods or different data is not exciting unless the hook is related to the specific population, data, method, etc.

---
class: inverse, center, middle
name: intro

# Starting the plan

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>

---
# Getting started

- Data management
- Preliminary analysis
- Aspirational introduction
- Draft paper
- See 3rd year workshop materials