---
title: "1st Year Workshop"
subtitle: "Tips for sticking around"
author: Ian McCarthy, Emory University
date: Economics PhD Professionalism Workshop #"`r format(Sys.time(), '%d %B %Y')`"
header-includes: 
  - \usepackage{graphicx}
  - \usepackage{amsmath}
  - \usepackage{includepdf}  
output:
#  html_document: default (toggle on for "simplified" view)
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom.css] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      beforeInit: ["macros.js","https://platform.twitter.com/widgets.js"]
---
class: inverse, center, middle
name: stay

# How to stay?

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=1055px></html>


<!-- Adjust some CSS code for font size, maintain R code font size -->
<style type="text/css">
.remark-slide-content {
    font-size: 30px;
    padding: 1em 2em 1em 2em;    
}
.remark-code, .remark-inline-code { 
    font-size: 20px;
}
</style>


<!-- Set R options for how code chunks are displayed and load packages -->
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
options(dplyr.summarise.inform = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center",  
  fig.height=3, #fig.width=6,
  # out.width="748px", #out.length="520.75px",
  dpi=300, #fig.path='Figs/',
  cache=T#, echo=F, warning=F, message=F
  )

knitr::opts_hooks$set(fig.callout = function(options) {
  if(options$fig.callout) {
    options$echo = FALSE
  }
  options
})

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, xaringanExtra, webshot)
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble(rgb(0.9, 0.5, 0.5))
```

---
# How to stay?

Conditional on a match, there are some definite dos and don'ts for succeeding in a PhD program.

---
# 1. Do...commit to the program

- This is your full time job
- Very different than life as an undergraduate or masters student

---
# 2. Do...take care of yourself

- (full time job, but...) need not be your entire life
- Self care is not selfish
- Counseling resources available from the university
- Potential for medical leave if necessary
- Come talk to me!

---
# 3. Do...work together

- You are not here to compete with one another. We want **EVERYONE** to succeed! Help each other.
- Celebrate each others' successes
- Think and talk about research ideas together

---
# 4. Do...stay organized

- Develop a study system and schedule
- Respond to emails
- Show up on time and be present


---
# 1. Don't...isolate yourself

- Get to know your students and faculty
- Social interactions, group study, etc. can be complementary to your classroom success


---
# 2. Don't...think academia is zero-sum

> "It's not enough that I should succeed. 
> Other's must fail"
>
> `r tufte::quote_footer('--- Ghengis Khan')`


---
# 3. Don't...lose confidence

- The first year is challenging and imposter syndrome is real
- You absolutely, 100%, **DESERVE TO BE HERE**


---
# A pep talk

.center[
<iframe width="800" height="500" src="https://www.youtube.com/embed/l-gQLqv9f4o?controls=0&amp;start=0&end=147" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
]

